Pricing Kernels and Risk Premia implied in Bitcoin Options

### 2024-01-07 written/paper.tex
writing

Insert Plot Funding Rate!!

>>>>

funding_btc_vs_eth_annualized_zoom.png
funding_btc_vs_eth_zoom.png
funding_btc_vs_eth_annualized.png
funding_btc_vs_eth.png

\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized.png}
    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized_zoom.png}

     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}

\end{minipage}
\begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth.png}
    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
    \centering
    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_zoom.png}
    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}

\end{minipage}
   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
